---
title: "Gymnastics Scoring"
author: "John Joyce"
date: "February 15, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Summary
The Gymnastics Scoring App extracts USAG Gymnastics Meet Information from the Meetscoresonline.com website for men and women gymnasts.
  
## Application Usage  
This basic application extracts USAG Gymnastics Meet Information from the Meetscoresonline.com website for men and women gymnasts.
It allows the user to input the "state" for the gymnastics meet that filters the results in the output report.
The output also provides plots showing the distribution of men's and women's meets by state.

```{r echo=FALSE, eval= TRUE, message=FALSE,warning=FALSE}
##  This application loads several packages to manipulate and output the data as needed.

    if (!require("shiny")) install.packages("shiny")
    if (!require("shinydashboard")) install.packages("shinydashboard")
    if (!require("leaflet")) install.packages("leaflet")
    if (!require("rvest")) install.packages("rvest")
    if (!require("dplyr")) install.packages("dplyr")
    if (!require("ggplot2")) install.packages("ggplot2")
    if (!require("XML")) install.packages("XML")
    if (!require("stringr")) install.packages("stringr")
    if (!require("tidyr")) install.packages("tidyr")
   
    library(shiny)
    library(shinydashboard)
    library(leaflet)
    library(rvest)
    library(dplyr)
    library(ggplot2)
    library(XML)
    library(stringr)
    library(tidyr)
```
## Data Analysis
This application reads a website (www.meetscoresonline.com) and parses the html code.
The data analysis includes reading and parsing the data and creates a data frame that contains meet information.
```{r echo=FALSE, eval = TRUE, message=FALSE,warning=FALSE}    
    ##  Load and store the url of the meetscoresonline.com website

    my_url <- "http://www.meetscoresonline.com/Results"

##  Parse the html code and use xml xpath functions to extract the desired fields.   

    webpage <- htmlParse(my_url)
    webroot <- xmlRoot(webpage)
    
    meet_list <- xpathSApply(webroot, "//table/..//tr", xmlGetAttr,"data-filter-by")
    meet_df <- do.call(rbind, meet_list) %>% as.data.frame()
    meet_df <- data.frame(lapply(meet_df, trimws), stringsAsFactors = FALSE)
    names(meet_df) <- c("meet")

##  Create new dataframe that extracts the gender and state for the meet name
    
    meet_df <- mutate(meet_df, 
                    gender = substr(meet,str_length(meet)-2,str_length(meet)),
                    state=substr(meet,str_length(meet)-6,str_length(meet)-5))
    
##  Extract the states for the gymnastics meets which will be used as input to the drop down list 
##  for the user to select.
    
    meet_states <- unique(meet_df$state) %>%
                      sort(meet_df$state, decreasing = FALSE) 
    
##  Parse the html code to find the website links containing the scores for each individual meet.  

    test_list <- as.list(xpathSApply(webroot, "//table/..//a",xmlGetAttr,"href"))
    test_df <- do.call(rbind, test_list) %>% as.data.frame()
    lst <- lapply(test_df, grep, pattern="/R", value=TRUE)
    combined_df <- cbind(meet_df, lst)
    combined_df <- mutate(combined_df,
                          site=paste("www.meetscoresonline.com",V1,sep=""))
    
```
A sample of the resulting extracted data frame is shown below:

```{r echo=FALSE, eval = TRUE, message=FALSE,warning=FALSE}    
    head(combined_df)    

```
##  Running the Application
The application can be used at the following location:
https://jjoyce1000.shinyapps.io/Gymnastics_Scoring/
